Predicting computational reproducibility of scientific pipelines using collaborative filtering

### 2018-04-19 paper.tex
Added the parameters to RFNU method
Removed Nf parameter for the RFNU

\paragraph{Random File Numbers (Uniform)- RFNU}
The number of files selected for every subject is randomly selected in a 
uniform distribution with parameters \textit{\textbf{a}} and \textit{\textbf{b}} where \textit{\textbf{a}} and \textit{\textbf{b}} are set as follows:\\
\textit{\textbf{a}} : The minimume random of file index that could be selected for a subject\\ 
\textit{\textbf{b}} : The highest possibility of file index that could be selected for a subject\\
$\mathbf{\alpha}$ : Training ratio\\
\textit{\textbf{Nf}} : Index file which means all files with lower and equal to this number should be sampled into the training set.
This method is realistic as files are sampled according to their production timestamps.
Due to sampling issues, it is possible that the actual training ratio obtained with this method
does not match the target one. We check that the difference between the target and real training ratios
was lower than 0.01.

>>>>

\paragraph{Random File Numbers (Uniform)- RFNU}
The number of files selected for every subject is randomly selected in a 
uniform distribution with parameters \textit{\textbf{a}} and \textit{\textbf{b}} where \textit{\textbf{a}} and \textit{\textbf{b}} are set as follows:\\
\textit{\textbf{a}} : The minimume random of file index that could be selected for a subject\\ 
\textit{\textbf{b}} : The highest possibility of file index that could be selected for a subject which is equal to the maximum index file (total number of subject's files,Nf)\\
$\mathbf{\alpha}$ : Training ratio\\
\[
  f(\alpha;p) =
  \begin{cases}
	  R(0,Nf)      & \text{if $\alpha \leq 0.5$ }, \\
	  R(\alpha,Nf),  
	  a = (2\alpha - 1) Nf & \text{if $\alpha > 0.5$}.
  \end{cases}
\]
This method is realistic as files are sampled according to their production timestamps.
Due to sampling issues, it is possible that the actual training ratio obtained with this method
does not match the target one. We check that the difference between the target and real training ratios
was lower than 0.01.
